\documentclass{article}

\begin{document}
    \title{Glass Nomad Documentation}

    \begin{titlepage}
        \maketitle
    \end{titlepage}

    \tableofcontents

    \newpage

    \section{Weapon Object}
    \begin{itemize}
        \item[Item Type - ] Whether the weapon is displayed as a primary or secondary weapon.
        \item[Fire Mode - ] Whether the weapon is able to fire in full auto or only single shot. Burst is not yet implemented.
        \item[Fire Rate - ] The minimum time in seconds between each shot.
        \item[Mag Size - ] The maximum number of bullets stored in a magazine.
        \item[Mag Count - ] The number of magazines the player can hold/ will spawn with.    
        \item[Range - ] The max range the weapon can hit an object at. Beyond this range the weapon will never hit. There is no drop off in damage.
        \item[Damage - ] The amount of damage the weapon does per hit.
        \item[Recoil Force - ] The value returned from the recoil curves is multiplied by this value. Controls how strong the recoil is.
        \item[Up Force Step - ] The increase along the Recoil Curve axis each time the weapon is fired.
        \item[Down Force Duration - ] The time it would take for the weapon to go from max recoil back to it's starting position.
        \item[Weapon Sound - ] The sound played when the weapon is fired.
        \item[Current Recoil Value - ] Hidden property. Used to track where on the x-axis of the recoil curves the weapon is currently at. Every time this value changes, the value on the y-axis for the old and new value is read. The difference between these values is then multiplied by Recoil Force, then applied to the weapon.
        \item[Recoil Curve Up - ] The upwards recoil curve for the weapon. Every time the weapon is fired, the Current Recoil Value is increased by Up Force Step.
        \item[Recoil Curve Down - ] The downwards recoil for this weapon. This force is applied each frame. It takes Down Force Duration number of seconds to go from a Current Recoil Value of one to a value of zero.
    \end{itemize}

\end{document}